---
title: "Online_Cryptography_Ads_Analysis_using_EDA"
author: "Christopher Toromo"
date: '2022-05-26'
output:
  pdf_document: default
  html_document: default
---

# 1. Defining the Question
## a) Specifying the Data Analytic Question
  
  To create a model to identify which individuals are most likely to click on ads. 
  
## b) Defining the Metric for Success

The study will be considered successful if we shall be able to get insight from the data using the Exploratory data analysis.

## c) Understanding the context
  Advertising is a means of communication with the users of a product or service. Advertisements are messages paid for by those who send them and are intended to inform or influence people who receive them. Advertising is always present, though people may not be aware of it. In today's world, advertising uses every possible media to get its message through. It does this via television, print (newspapers, magazines, journals etc), radio, press, internet, direct selling, hoardings, mailers, contests, sponsorships, posters, clothes, events, colours, sounds, visuals and even people (endorsements). In our model, we shall try to predict the probabilty of a person clicking on an ad.
  
## d). Recording the Experimental Design
  
  We will use exploratory data analysis, such as Univariate and Bivariate in this study to determine the relationships and differences between different variables.

## e) Data Relevance

  The dataset to use for this project can be found by following this link:
  https://www.bit.ly/IPAdvertisingData
  

# 2. Reading the Data

```{r}

advertising <- read.csv("https://www.bit.ly/IPAdvertisingData")

```
 
# 3. Checking the Data

## a) Checking the top data

```{r}
head(advertising)
```
## b). Checking the bottom data

```{r}
tail(advertising)
```


## c). Checking the Structure of the Dataset
  
```{r}
str(advertising)
```
  
## d). Checking the shape of our data

```{r}
dim(advertising)
```
We have 1000 rows and 10 columns in our dataset


# 4. Tidying the Dataset

## a). Checking the Missing Values

```{r}
colSums(is.na(advertising))
```

From the above, we can see that we do not have Missing Values in the dataset.

## b). Checking for Duplicate Values

```{r}
duplicated_rows <- advertising[duplicated(advertising),]

duplicated_rows
```

We can also see that we have 0 rows containing duplicates values. This is very import for the consitency of data.

## c). Checking for Outliers

We shall use Boxplot to check for outliers in our numeric features

```{r}
# Selecting Numeric columns

library("dplyr")

# getting numeric columns using dplyr() function             
numeric_col <- select_if(advertising, is.numeric)

head(numeric_col)
```
```{r}
# Plotting Boxplot for the Numeric columns

boxplot(numeric_col,main="BoxPlot for the Numeric Features", col="darkgreen")
```
We can clearly see we have outliers in our Area.Income feature. We shall be removing the outlier using the Interquartile Range Method

```{r}
outliersValue <- boxplot.stats(advertising$Area.Income)$out

advertising$Area.Income[!advertising$Area.Income %in% outliersValue]

```

# 5. Exploratory Data Analysis

## a) Univariate Analysis

We shall use the Graphical method to do the Univeriate Analysis

### i). Measures of Central Tendency

```{r}
# Mean Age

mean(advertising$Age)

```
We can see the average age is aroung 36 years

```{r}
# Median Age

median(advertising$Age)

```
The median age is 35 years

```{r}
# Average Daily spent on Site

mean(advertising$Daily.Time.Spent.on.Site)

```
```{r}
mean(advertising$Daily.Internet.Usage)
```
```{r}
# Mode of Area Income

mode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

mode(advertising$Area.Income)

```
The modal Area Income is 61833


### ii). Measures of Dispersion

```{r}
# Checking the range of the Numeric columns of the Area Income

range(advertising$Area.Income)

```

```{r}
# Checking the maximum age

max(advertising$Age)
```
```{r}
# Checking the minimum age

min(advertising$Age)
```
```{r}
# Checking the Variance of the Area Income

var(advertising$Area.Income)

```
```{r}
# Checking the Standard Deviation of the Area Income

sd(advertising$Area.Income)

```
### iii) Univariate Graphical

We shall be using the box plot to display our age data

```{r}
# Boxplot for age

boxplot(advertising$Age,col="gold")
```
We shall use bar graph to show the gender(Male) feature of our data

```{r}
gender_frequency <- table(advertising$Male)

barplot(gender_frequency, main = "Bargraph for Gender")
```
We have slightly more females than males as clearly shown on the bargraph. The 0 implies Female while 1 implies male


```{r}
# Histogram to show the Daily Internet Usage

hist(advertising$Daily.Internet.Usage, main = "Histogram for Daily Internet Usage")
```

## b). Bivariate Analysis

### i). Covariance

```{r}
cov(numeric_col)
```

### ii). Correlation

```{r}
cor(numeric_col)
```

We shall now visualize the correlation matrix

```{r}
# Loading the corrplot 

library(corrplot)

```
```{r}

# Dropping the Male from numeric column

num_col <- subset(numeric_col, select = -c(Male))


corr_matrix <- cor(num_col)

corrplot(corr_matrix, method='number')
  
```
From the above Correlation Matrix, we can see there is strong inverse correction between Daily Internet Usage and Clicked on Ad.


### iii). Scatterplot

We shall use the scatterplot to show the relationship between Area Income and Daily Internet Usage

```{r}

area_income <- advertising$Area.Income
daily_usage <- advertising$Daily.Internet.Usage

plot(area_income,daily_usage,xlab="Area Income", ylab="Daily Internet Usage",main="Scatterplot for Area Income and Daily Internet usage")

```

# 6. Conclusion and Recommedation

From our Exploratory Data Analysis, we can easily see the relation between the various features of our dataset.We have seen that older people are more likely to click on the ads this is because there is a positive correlation between age and click on ad. Hence the entrepreneur should focus more on older people. Also we have seen that with increase on Daily Internet Usage, there is a huge reduction dlick on ads, this implies the entrepreneur should focus more on individual with low daily internet usage.

# 7. Follow up questions
## a) Did we have the right data?
Yes, the dataset available for this analysis was relevant to the research problem.

## b) Do we need other data to answer the research question?
No, the dataset provided had relevant information for the research question.